Molecular Analysis

### 2023-12-04 analysis/aud_analysis.Rmd
comparison with mcid12 doc style files

save_plot(coughs_pl, 
          pdf_file = "../results/cough-data/coughs-frequency-by-condition.pdf", 
          eps_file = "../results/cough-data/coughs-frequency-by-condition.eps", 
          w = 7.25, h = 6)
```

>>>>

save_plot(coughs_pl, 
          pdf_file = "../results/cough-data/coughs-frequency-by-condition.pdf", 
          eps_file = "../results/cough-data/coughs-frequency-by-condition.eps", 
          w = 7.25, h = 6)

ggsave(plot = coughs %>%
            mutate(coughs_per_min = n_coughs / TT) %>%
            mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
            ggplot(aes(x = aircleaner, fill = aircleaner, y = coughs_per_min)) +
            geom_boxplot2(width.errorbar = .3, width = .4) +
            ggsignif::geom_signif(annotations = "Posterior prob. = 93%", y_position = 6.25, xmin = 1, xmax = 2, 
                                  textsize = 40 / cm(1), vjust = -.5) +
            scale_fill_manual(values = c(bluegrey[1], "#E4003C")) +
            scale_y_continuous(limits = c(0, NA), expand = expansion(add = c(0, .66))) +
            labs(y = "Number of coughs per min", x = "Air cleaner") +
            theme_custom() +
            theme(legend.position = "none",
                  axis.text = element_text(size = 40),
                  axis.title = element_text(size = 40)), 
          filename = "../results/cough-data/coughs-frequency-by-condition-large.png", 
          width = 4 * 7.25 / cm(1), height = 4 * 6  / cm(1))
```

### 2023-12-04 analysis/env_analysis.Rmd
comparison with mcid12 doc style files

save_plot(boxpl_cn, 
          pdf_file = "../results/env-data/aerosol-number-boxplot.pdf", 
          eps_file = "../results/env-data/aerosol-number-boxplot.eps", 
          w = 7.25, h = 6)
```

>>>>

save_plot(boxpl_cn, 
          pdf_file = "../results/env-data/aerosol-number-boxplot.pdf", 
          eps_file = "../results/env-data/aerosol-number-boxplot.eps", 
          w = 7.25, h = 6)

ggsave(plot = env_epi_data %>%
  dplyr::select(class, date, aircleaner, Cn) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = Cn)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "Posterior prob. = 100%", y_position = 240, xmin = 1, xmax = 2, 
                        textsize = 40 / cm(1), vjust = -.5) +
  scale_fill_manual(values = c(bluegrey[1], "#E4003C")) +
  scale_y_continuous(expand = expansion(add = c(0, 30)), limits = c(0, NA)) +
  labs(title = "a", y = expression("Aerosol concentration (1/cm"^3*")"), x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot") +
  theme(plot.title.position = "plot",
        axis.text = element_text(size = 40),
        axis.title = element_text(size = 40)) +
  guides(fill = "none"),
  filename = "../results/env-data/aerosol-number-boxplot-large.png",
  width = 4 * 7.25 / cm(1), height = 4 * 6 / cm(1) )
```

### 2023-12-04 analysis/epi_analysis.Rmd
minor fix
comparison with mcid12 doc style files

save_plot(cases_by_cond_pl,
          pdf_file = "../results/epi-data/cases_by_condition.pdf",
          eps_file = "../results/epi-data/cases_by_condition.eps",
          w = 7.25, h = 6) 
```

@@

avoid_infections

>>>>

save_plot(cases_by_cond_pl,
          pdf_file = "../results/epi-data/cases_by_condition.pdf",
          eps_file = "../results/epi-data/cases_by_condition.eps",
          w = 7.25, h = 6)

ggsave(plot = epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = cases), size = 40 / cm(1), vjust = -1) +
  ggsignif::geom_signif(annotations = "Posterior prob. = 91%", y_position = 27, xmin = 1, xmax = 2, 
                        textsize = 40 / cm(1), vjust = -.5, tip_length = .075) +
  labs(x = "Air cleaner", y = "Number of respiratory cases", fill = "Air cleaner", title = "b") +
  scale_fill_manual(values = c(bluegrey[1], "#E4003C")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none") +
    theme(legend.position = "none",
                  axis.text = element_text(size = 40),
                  axis.title = element_text(size = 40)),
  filename = "../results/epi-data/cases_by_condition_large.png",
  width = 4 * 7.25 / cm(1), height = 4 * 6 / cm(1))
```

@@

avoid_infections %>%
  mutate_if(is.numeric, round, 0)

### 2023-12-04 analysis/mol_analysis.Rmd
comparison with mcid12 doc style files

save_plot(pos_cond_pl, 
          "../results/mol-data/saliva-by-study-condition.pdf",
          "../results/mol-data/saliva-by-study-condition.eps",
          w = 7.25, h = 6)
```

>>>>

save_plot(pos_cond_pl, 
          "../results/mol-data/saliva-by-study-condition.pdf",
          "../results/mol-data/saliva-by-study-condition.eps",
          w = 7.25, h = 6)

ggsave(plot = pos_cond_pl <- df_pos_stud %>%
  ggplot(aes(x = aircleaner, y = n_pos)) +
  geom_bar(mapping = aes(fill = aircleaner), stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = n_pos), size = 40 / cm(1), vjust = -1) +
  geom_segment(data = data.frame(x = .5, xend = .5, y = 30, yend = 29), 
               mapping = aes(x = x, xend = xend, y = y, yend = yend), color = "white") +
  ggsignif::geom_signif(annotations = "Posterior prob. = 65%", y_position = 30, xmin = 1, xmax = 2, 
                        textsize = 40 / cm(1), vjust = -.5, tip_length = .1) +
  labs(x = "Air cleaner", y = "Number of positive saliva samples") +
  scale_fill_manual(values = c(bluegrey[1], "#E4003C")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot",
        axis.text = element_text(size = 40),
        axis.title = element_text(size = 40)) +
  guides(fill = "none"),
  filename = "../results/mol-data/saliva-by-study-condition-large.png",
  width = 4 * 7.25 / cm(1), height = 4 * 6 / cm(1))
```
